Incremental Forward Reasoning for White-Box~Proof~Search

### 2025-02-24 paper.tex
Use λ x. t instead of λ x, t
Weaken claims about ACL2 and PVS; clarify trigger terms

\newcommand{\Lam}[2]{\ensuremath{\lambda\, #1,\; #2}}
\newcommand{\All}[2]{\ensuremath{\forall\, #1,\; #2}}
\newcommand{\mvar}[1]{\ensuremath{{?#1}}}
\newcommand{\Prop}{\ensuremath{\mathrm{Prop}}}
\newcommand{\vars}{\ensuremath{\mathrm{svars}}}
\newcommand{\dom}{\ensuremath{\mathrm{dom}}}
\newcommand{\sub}{\ensuremath{\mathrm{sub}}}
\newcommand{\lvl}{\ensuremath{\mathrm{lvl}}}
\newcommand{\Rules}{\ensuremath{\mathcal{R}}}
\newcommand{\Hyps}{\ensuremath{\mathcal{H}}}
\newcommand{\States}{\ensuremath{\mathcal{S}}}
\newcommand{\CMatches}{\ensuremath{\mathcal{C}}}
\newcommand{\addHyp}{\ensuremath{\mathrm{addHyp}}}
\newcommand{\delHyp}{\ensuremath{\mathrm{delHyp}}}
\newcommand{\addMatch}{\ensuremath{\mathrm{addMatch}}}
\newcommand{\powerset}{\ensuremath{\mathcal{P}}}

@@

\para{White-Box Tactics.}
Among white-box proof automation tactics, to our knowledge only ACL2's \enquote{waterfall}~\cite{ACL2} and PVS's various proof search strategies~\cite{PVS} have special support for forward reasoning.
Both use essentially Aesop's naive algorithm, i.e.\ the context of each goal is saturated independently without reusing partial results from other goals.
ACL2 additionally supports \emph{trigger terms}, which allow forward rules to be selected based on the presence of a particular term anywhere in the goal, rather than based on particular hypotheses.
Aesop implements a similar mechanism, \emph{rule patterns}, not described here due to space constraints.

The auto2 tactic~\cite{auto2} employs an SMT-like search procedure based on forward reasoning and e-matching~\cite{simplify}.
As such, it does not require incrementality, but it could perhaps benefit from indexing along the lines of our variable indices.
Many other white-box tactics can execute arbitrary tactics, including forward rules, but make no special provisions for them.

>>>>

\newcommand{\Lam}[2]{\ensuremath{\lambda\, #1.\; #2}}
\newcommand{\All}[2]{\ensuremath{\forall\, #1,\; #2}}
\newcommand{\mvar}[1]{\ensuremath{{?#1}}}
\newcommand{\Prop}{\ensuremath{\mathrm{Prop}}}
\newcommand{\vars}{\ensuremath{\mathrm{svars}}}
\newcommand{\dom}{\ensuremath{\mathrm{dom}}}
\newcommand{\sub}{\ensuremath{\mathrm{sub}}}
\newcommand{\lvl}{\ensuremath{\mathrm{lvl}}}
\newcommand{\Rules}{\ensuremath{\mathcal{R}}}
\newcommand{\Hyps}{\ensuremath{\mathcal{H}}}
\newcommand{\States}{\ensuremath{\mathcal{S}}}
\newcommand{\CMatches}{\ensuremath{\mathcal{C}}}
\newcommand{\addHyp}{\ensuremath{\mathrm{addHyp}}}
\newcommand{\delHyp}{\ensuremath{\mathrm{delHyp}}}
\newcommand{\addMatch}{\ensuremath{\mathrm{addMatch}}}
\newcommand{\powerset}{\ensuremath{\mathcal{P}}}

@@

\para{White-Box Tactics.}
Among white-box proof automation tactics, to our knowledge only ACL2's \enquote{waterfall}~\cite{ACL2} and PVS's various proof search strategies~\cite{PVS} have special support for forward reasoning.
Both use techniques similar to Aesop's naive algorithm; in particular, the context of each goal is saturated independently.
ACL2 additionally allows forward rules to be annotated with \emph{trigger terms}, which cause the rules to be run if the trigger terms are matched anywhere in a goal.
Aesop implements a similar mechanism, \emph{rule patterns}, not described here due to space constraints.

The auto2 tactic~\cite{auto2} employs an SMT-like search procedure based on forward reasoning and e-matching~\cite{simplify}.
As such, it does not require incrementality, but it could perhaps benefit from indexing along the lines of our variable indices.
